Untitled

### 2025-01-17 log.Rmd
update some of the test fixtures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Date: 
clipr::write_clip(paste0('## ', format(Sys.time(), "%F (%A %B %e)\n\n")))
# Date and time:
clipr::write_clip(paste0('## ', format(Sys.time(), "%F %X %Z (%A %B %e)\n\n")))
```
## 2024-10-16 (Wednesday October 16)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Date: 
clipr::write_clip(paste0('## ', format(Sys.time(), "%F (%A %B %e)\n\n")))
# Date and time:
clipr::write_clip(paste0('## ', format(Sys.time(), "%F %X %Z (%A %B %e)\n\n")))
```

## 2024-12-02

Global Names Verifier is the new version of Global Names Resolver, according to Matthias Grenie.

## 2024-10-16 (Wednesday October 16)
